How did the introduction of Stemmed Points affect Mobility and Site Occupation during the Late Pleistocene in Korea?

### 2020-12-04 analysis/paper/paper.Rmd
put here to 001 Rscript

<!---```{r korea-map, fig.cap="Site map. Korean Paleolithic sites mentioned in the text."}
source(here::here("analysis/paper/001-draw-the-map.R"))
knitr::include_graphics(here::here("analysis/figures/001-site-map.png"))
``` --->

>>>>

```{r korea_map, fig.cap="Site map. Korean Paleolithic sites mentioned in the text."}
source(here::here("analysis/paper/001-draw-the-map.R"))
knitr::include_graphics(here::here("analysis/figures/001-site-map.png"))
```
